# Ensemble Network Aggregation

## Define Simulation Settings

```{r globals}
SIZE <- c("tiny","small","moderate","middle","large")
NP <- as.character(c(20, 50, 100, 200, 500, 1000))
NOISE <- as.character(c(0.25, 0.5, 1, 1.5))
BOOTSTRAP_COUNT <- 140

set.seed(1234)
library(knitr)
```


## Simulate Networks

```{r simulate, results='hide', message=FALSE, echo=FALSE, cache=TRUE}
sim <- knit_child("simulate/simulateNetworks.Rmd", eval=TRUE)
```

`r paste(sim, collapse = '\n')`


## Rebuild Networks

```{r rebuild, results='hide', message=FALSE, echo=FALSE, cache=TRUE}
rebuild <- knit_child("rebuild/rebuildNetworks.Rmd", eval=TRUE)
```

`r paste(rebuild, collapse = '\n')`


## Calculate Area Under the ROC Curve
 
```{r aucs, results='hide', message=FALSE, echo=FALSE, cache=TRUE}
aucs <- knit_child("aucs/calcAUCs.Rmd", eval=TRUE)
```

`r paste(aucs, collapse = '\n')`


## Merge Datasets

```{r mergeDS, results='hide', message=FALSE, echo=FALSE, cache=TRUE}
mergeDS <- knit_child("dataset-merge/merge.Rmd", eval=TRUE)
```

`r paste(mergeDS, collapse = '\n')`


## Test Bootstrapping

```{r bootstrap, results='hide', message=FALSE, echo=FALSE, cache=TRUE}
boots <- knit_child("bootstrap/bootstrap.Rmd", eval=TRUE)
```

`r paste(boots, collapse = '\n')`

Copyright ©2012-2013, The University of Texas Southwestern Medical Center. All rights reserved.