This section will test the reconstruction of three different datasets using a naive merging approach and a meta-analysis approach based on ENA.

First, we'll read in three simulated datasets.

```{r}
#' Create a simulated randomized "true" regulatory network based on the truth file provided.
#' @param size should be one of c("tiny","small","moderate","middle","large", "huge")
#' @author Jeffrey D. Allen \email{Jeffrey.Allen@@UTSouthwestern.edu}
randomizeRegulation <- function(size){
	dat <- read.csv(paste("../truth/", size,".csv",sep=""))

	dat <- dat[dat$Source != dat$Target,]
	dat[dat$Source > dat$Target,] <- dat[dat$Source > dat$Target,2:1]
	dat[dat$Source > dat$Target,]

	N <- dim(dat)[1]
	dat$regulation <- round(sign(rbinom(N, 1, 0.5) - 0.5)*rnorm(N,0.5,0.2) ,2)
	dat$type <- sign(dat$regulation)	

	dat
}


#' Read the edge definition and simulate the regulation ###
#'
#' @param dat the regulatory truth obtained from randomizeRegulation()
#' @param sample can be any positive number. 
#' @param noise  can be any positive number (for our study, we should try 0.25, 0.5, 0.75, 1, 1.5 and 2) 
#' @author Jeffrey D. Allen \email{Jeffrey.Allen@@UTSouthwestern.edu}
network.simulation <- function(dat, sample, noise)
{
	
	
	Gene <- union(dat$Source,dat$Target)
	nGene <- length(Gene)
	
	#### initiate the matrix expr to store the simulated expression level ####


	nSamp <- sample
	expr <- matrix(0,nGene, nSamp)
	rownames(expr) <- Gene
	colnames(expr) <- paste("S", 1:nSamp, sep="")

	sigma <- noise

	unknown <- unique(dat$Target)
	known <- setdiff(Gene, unknown)

	for(i in known)
	{
		expr[as.character(i),] <- rbinom(nSamp,1,0.5)*2 + rnorm(nSamp,0,sigma) - 1
	}

	while(length(unknown) > 0)
	{
		for(i in unknown)
		{			
			source <- as.character(dat$Source[dat$Target == i])
			if(all(source %in% known)) 
			{ 				
				val <- ifelse(rep(length(source) == 1,nSamp), 
					expr[as.character(source),]*dat[dat$Target == i,3] ,
					dat[dat$Target == i,3] %*% expr[as.character(source),])
				expr[as.character(i),] <- as.numeric(val > 0.0)*2-1 + rnorm(nSamp,0,sigma)
			 	known <- append(known,i)
				unknown <- setdiff(unknown, i) 
			}
		}	
	}
  	
	round(expr, 2)
}

reg <- randomizeRegulation("middle")
sim25 <- network.simulation(reg, 200, 0.25)
sim1 <- network.simulation(reg, 200, 1)
sim2 <- network.simulation(reg, 200, 2)
```


```{r loadpack, results='hide', message=FALSE}
library(WGCNA)
library(GeneNet)
library(space)
library(ENA)
library(ROCR)
```

We'll first need a function to extract the true network for inclusion in our aggregated tables.

```{r}
#' Convert an adjacency-like list (which may or may not contain all the gene 
#' IDs in the network) into an adjacency matrix.
#' 
#' @param IDs A vector of Gene IDs in this network
#' @param truthList An adjacency list containing the truth to be converted 
#' to a matrix. Should have vectors for "Source", "Target", and "Regulation."
#' @author Jeffrey D. Allen \email{Jeffrey.Allen@@UTSouthwestern.edu}
truthToMat <- function(IDs, truthList){
	truth <- matrix(0, ncol=length(IDs), nrow=length(IDs))
	rownames(truth) <- IDs
	colnames(truth) <- IDs
	diag(truth) <- 1;
	for (i in 1:dim(truthList)[1]){
		s <- truthList[i,]$Source
		t <- truthList[i,]$Target
		r <- truthList[i,]$regulation
		truth[which(IDs == s), which(IDs == t)] <- r
	}
	truth <- symmetricize(truth, "ud")
	return (truth)
}
```

We'll then need a helper function which, given all of the information about a simulation, can extract the simulated dataset, aggregate the results into a table, and write the output.

```{r processMatricesMer}
#' Read and process an expression matrix using all three methods and ENA 
#' and return the generated results.
#' @param simul The simulated expression data
#' @param bootstrapCount The number of iterations to perform while bootstrapping.
#' @param bootstrapPercentage The percentage of available samples to include in each
#' bootstrapped iteration.
#' @param Cluster an MPI cluster to which we can distribute the work.
#' @param truth The truth for the network -- can be combined into the resultant
#' output for easier analysis of performance later.
#' @author Jeffrey D. Allen \email{Jeffrey.Allen@@UTSouthwestern.edu}
processMat <- function(simul, bootstrapCount=140, bootstrapPercentage = 0.7, cluster, truth){
	
	addressing <- getTableAddressing(rownames(simul), truth)
			
	sp <- bootstrap(simul, "buildSpace", cluster=cluster, iterations = bootstrapCount, sample.percentage = bootstrapPercentage)	
	wg <- symmetricize(abs(buildWgcna(simul)))
	wg <- wg[upper.tri(wg)]
	gn <- bootstrap(simul, "buildGenenet", cluster=cluster, iterations = bootstrapCount, sample.percentage = bootstrapPercentage)
			
	joint1 <- ena(cbind(gn[,3], wg, sp[,3]))
	joint1 <- data.frame(addressing, sp[,3], wg, gn[,3], joint1, row.names=NULL)
	colnames(joint1) <- c("Source", "Dest", "Truth", "BootstrappedSPACE", "WGCNA", "BootstrappedGenenet", "ENA")
	#Since this graph is undirected, for consistency, make Source always smaller than Dest
	allGenes <- union(joint1$Source, joint1$Dest)
	levels(joint1$Source) <- allGenes
	levels(joint1$Dest) <- allGenes
	joint1[as.character(joint1[,1]) > as.character(joint1[,2]),1:2] <- joint1[as.character(joint1[,1]) > as.character(joint1[,2]),2:1]
	
	return(joint1)
}
```
		
		
We'll want to grab the truth for this network:

```{r}
truthList <- read.csv(paste("../truth/truth middle.csv", sep=""));
truth <- truthToMat(rownames(sim2), truthList)

```
		
### Individual Network Reconstruction
		
We'll now reconstruct each of these networks individually.

```{r calcAUCsMer, message=FALSE, results='hide'}
cluster <- NULL
if (require(Rmpi) && require(snow)){
	invisible(capture.output(cluster <- makeCluster(mpi.universe.size()-1, type="MPI")))	
	warning(paste("Distributing bootstrapped networks across a cluster of", mpi.universe.size()-1, "CPUs."))
}
```

```{r}
net25 <- processMat(sim25, cluster=cluster, truth=truth)
net1 <- processMat(sim1, cluster=cluster, truth=truth)
net2 <- processMat(sim2, cluster=cluster, truth=truth)
```

### Merged Network Reconstruction

We'll now want to compute the merged networks using either the naive method or the meta-analysis ENA method. We'll perform the naive first by just stacking the three simulations on top of one another.

```{r}
stackedSim <- cbind(sim25, sim1, sim2)
stackedNet <- processMat(stackedSim, cluster=cluster, truth=truth)
```

And the alternative ENA method can be performed by joining the three previous results.

```{r}
enaNet <- ena(cbind(net25$ENA, net1$ENA, net2$ENA))

save(enaNet, stackedNet, net25, net1, net2, file="nets.Rda")
```

### Performance Review

We can now calculate the the ROCs/AUCs of these networks.

```{r}
truVec <- net25$Truth != 0
pred25 <- prediction(net25$ENA, truVec)
perf25 <- performance(pred25, "tpr", "fpr")
performance(pred25, "auc")@y.values[[1]]

pred1 <- prediction(net1$ENA, truVec)
perf1 <- performance(pred1, "tpr", "fpr")
performance(pred1, "auc")@y.values[[1]]

pred2 <- prediction(net2$ENA, truVec)
perf2 <- performance(pred2, "tpr", "fpr")
performance(pred2, "auc")@y.values[[1]]

predStac <- prediction(stackedNet$ENA, truVec)
perfStac <- performance(predStac, "tpr", "fpr")
performance(predStac, "auc")@y.values[[1]]

predENA <- prediction(enaNet, truVec)
perfENA <- performance(predENA, "tpr", "fpr")
performance(predENA, "auc")@y.values[[1]]
```

And plot them
```{r}
plot(perfENA, col=1, lwd=2)
plot(perfStac, col=2, lwd=2, add=TRUE)
plot(perf25, col=3, add=TRUE)
plot(perf1, col=4, add=TRUE)
plot(perf2, col=5, add=TRUE)
legend(.1, .4, 
			 c("ENA", 
			 	"Simple Merge", 
			 	expression(paste("Individual Network, ", sigma,"=0.25", sep="")), 
			 	expression(paste("Individual Network, ", sigma,"=1", sep="")), 
			 	expression(paste("Individual Network, ", sigma,"=2", sep=""))), col=1:5, lwd=c(2,2,1,1,1)) 
```









