This section will document the construction of the networks for all of the considered methods on all of the simulated datasets.

### Loading Packages

We'll load in all the relevant packages. `parmigene` is a package created to allow R users to work with Aracne. `bnlearn` is a package that implements a variety of Bayesian methods. `WGCNA`, `space`, and `GeneNet` all implement partial-correlation or correlation-based learning methods and will be identified by their package name for the duration of the study. All of these packages are supported by our `ENA` package which offers helper functions for all of these packages.

```{r load, results='hide', message=FALSE}
library(WGCNA)
library(GeneNet)
library(space)
library(ENA)
```

### Process Simulated Networks

We'll first need a function to extract the true network for inclusion in our aggregated tables.

```{r}
#' Convert an adjacency-like list (which may or may not contain all the gene 
#' IDs in the network) into an adjacency matrix.
#' 
#' @param IDs A vector of Gene IDs in this network
#' @param truthList An adjacency list containing the truth to be converted 
#' to a matrix. Should have vectors for "Source", "Target", and "Regulation."
#' @author Jeffrey D. Allen \email{Jeffrey.Allen@@UTSouthwestern.edu}
truthToMat <- function(IDs, truthList){
	truth <- matrix(0, ncol=length(IDs), nrow=length(IDs))
	rownames(truth) <- IDs
	colnames(truth) <- IDs
	diag(truth) <- 1;
	for (i in 1:dim(truthList)[1]){
		s <- truthList[i,]$Source
		t <- truthList[i,]$Target
		r <- truthList[i,]$regulation
		truth[which(IDs == s), which(IDs == t)] <- r
	}
	truth <- symmetricize(truth, "ud")
	return (truth)
}
```

We'll then need a helper function which, given all of the information about a simulation, can extract the simulated dataset, aggregate the results into a table, and write the output.

```{r processMatrices}
#' Read and process an expression matrix using all three methods and ENA 
#' and return the generated results.
#' @param size The size of the network to use ("tiny", "small", etc.)
#' @param ns The number of samples in the desired dataset.
#' @param dataDir Where to find the expression data.
#' @param bootstrapCount The number of iterations to perform while bootstrapping.
#' @param bootstrapPercentage The percentage of available samples to include in each
#' bootstrapped iteration.
#' @param Cluster an MPI cluster to which we can distribute the work.
#' @param truth The truth for the network -- can be combined into the resultant
#' output for easier analysis of performance later.
#' @author Jeffrey D. Allen \email{Jeffrey.Allen@@UTSouthwestern.edu}
processMat <- function(size, ns, sigma, dataDir, bootstrapCount, bootstrapPercentage = 0.7, cluster, truth){
	simul <- read.csv(paste(dataDir,size, "nSamp", ns, "Sigma", sigma, ".csv",sep=""), row.names=1)	
	
	addressing <- getTableAddressing(rownames(simul), truth)
			
	sp <- bootstrap(simul, "buildSpace", cluster=cluster, iterations = bootstrapCount, sample.percentage = bootstrapPercentage)	
	wg <- symmetricize(abs(buildWgcna(simul)))
	wg <- wg[upper.tri(wg)]
	gn <- bootstrap(simul, "buildGenenet", cluster=cluster, iterations = bootstrapCount, sample.percentage = bootstrapPercentage)
			
	joint1 <- ena(cbind(gn[,3], wg, sp[,3]))
	joint1 <- data.frame(addressing, sp[,3], wg, gn[,3], joint1, row.names=NULL)
	colnames(joint1) <- c("Source", "Dest", "Truth", "BootstrappedSPACE", "WGCNA", "BootstrappedGenenet", "ENA")
	#Since this graph is undirected, for consistency, make Source always smaller than Dest
	allGenes <- union(joint1$Source, joint1$Dest)
	levels(joint1$Source) <- allGenes
	levels(joint1$Dest) <- allGenes
	joint1[as.character(joint1[,1]) > as.character(joint1[,2]),1:2] <- joint1[as.character(joint1[,1]) > as.character(joint1[,2]),2:1]
	
	return(joint1)
}
```

Finally, we'll loop through all of the simulated datasets to construct all of the networks associated. We'll simulate on 6 network sizes, 6 numbers of samples, and 6 noise values, for $6^3=216$ total datasets. If we're able to load the `Rmpi` and `snow` packages, we'll assume we are to distribute the load across a cluster. Otherwise, we'll just run it in this R process in a traditional way.

```{r message=FALSE, results='hide'}
cluster <- NULL
if (require(Rmpi) && require(snow)){
	invisible(capture.output(cluster <- makeCluster(mpi.universe.size()-1, type="MPI")))	
	warning(paste("Distributing bootstrapped networks across a cluster of", mpi.universe.size()-1, "CPUs."))
}

dataDir <- "../data/simulations/"
dir.create("../data/results-ena/")

for (size in SIZE){
	truthList <- read.csv(paste("../truth/truth ", size, ".csv", sep=""));
	simul <- read.csv(paste(dataDir,size, "nSamp", NP[1], "Sigma", NOISE[1], ".csv",sep=""), row.names=1)	
	truth <- truthToMat(rownames(simul), truthList)

	for (ns in NP){
		for (sigma in NOISE){
			results <- processMat(size, ns, sigma, dataDir, BOOTSTRAP_COUNT, cluster=cluster, truth=truth)				
			saveRDS(results, file=paste("../data/results-ena/",size,"nSamp",ns,"Sigma",sigma,".Rds",sep=""))
		}
	}
}
```